---
title: CDS 411 course materials
---

```{r setup, include = FALSE}
source("../R/rmarkdown_setup.R")
options(knitr.kable.NA = "")
topic_schedule <- readr::read_csv("../data/calendar.csv")
readings <- readr::read_csv("../data/readings.csv")
software <- readr::read_csv("../data/software.csv")
homeworks <- readr::read_csv("../data/homeworks.csv")
datacamp_cheat_sheets <- readr::read_csv("../data/datacamp_cheat_sheets.csv")
```

*   [Topic schedule](#topic-schedule)
*   [Readings](#readings)
*   [Homeworks](#homeworks)
*   [Final project](#final-project)
*   [Resources and links](#resources-and-links)
    *   [Datacamp cheat sheets](#datacamp-cheat-sheets)
    *   [Software](#software)
*   [License](#license)

## Topic schedule

```{r topic-schedule, echo = FALSE}
knitr::kable(
  x = topic_schedule,
  format = "pandoc",
)
```

## Readings

```{r readings, echo = FALSE}
knitr::kable(
  x = readings,
  format = "pandoc"
)
```

## Homeworks

```{r homeworks, echo = FALSE}
knitr::kable(
  x = homeworks,
  format = "pandoc"
)
```

## Final project

**Instructions:** [project/final\_project.md](project/final_project.md)  

## Resources and links

### Datacamp cheat sheets

[Datacamp][datacamp-url] has put together a series of [*Python for Data Science* cheat sheets][datacamp-cheat-sheets-url] that you can use as a quick reference during the class.
The most relevant ones have been downloaded to this repository and are linked below:

```{r datacamp-cheat-sheets, echo = FALSE}
knitr::kable(
  x = datacamp_cheat_sheets,
  format = "pandoc"
)
```

### Software

The following software is not required for participating in the course, but may be useful in your workflow.

```{r software, echo = FALSE, results = 'asis'}
knitr::kable(
  x = software,
  format = "html",
  escape = FALSE
)
```

## License

[![Creative Commons License][cc-by-sa-4-img]][cc-by-sa-4]

Unless otherwise noted, the course materials in this repository are licensed under a [Creative Commons Attribution-ShareAlike 4.0 International License][cc-by-sa-4].

[cc-by-sa-4]:                http://creativecommons.org/licenses/by-sa/4.0/
[datacamp-url]:              https://datacamp.com
[cc-by-sa-4-img]:            https://i.creativecommons.org/l/by-sa/4.0/88x31.png
[datacamp-cheat-sheets-url]: https://www.datacamp.com/community/data-science-cheatsheets
